---
title: "Relationship Between Size Measurements of Penguins and the Island That They Live On"
author: "Amara Miller"
date: "`r format(Sys.Date())`"
output: github_document
---

## Install Packages and Read Data 

```{r}
library(tidyverse)
library(palmerpenguins)
penguins_data <- penguins
penguins_data
```


## Abstract

From the Palmer Penguins site, there were two datasets that could be explored. The penguin dataset is what is going to be explored for this project. The main purpose of this dataset is to give an example of great data to use for analysis and visualization. Many different variables are provided when the data is being presented. It is important to be able to  compare the size measurements of three different species of penguins on three different islands in Antarctica. To be specific this project will be more focused on how the size measurements vary compared to what islands that they live on. To accomplish this goal, the data analysis software of RStudio will be utilized. This will be helpful when downloading all of the data that is needed and when creating graphs to compare measurements. From there, the next step would be to have one measurement on the x-axis and one measurement on the y-axis and then add what islands the penguins are located on to see if there is a correlation. 

## Introduction


## Methods

- Data was taken from a website called "Palmer Penguins", which contains information about penguins on islands in Antartica
- From the two datasets on the website, the penguins data is what was used
- The packages of tidyverse and palmerpenguins were then installed and the data was read into RStudio
- A few graphs were then created for visual aid to look closer and to compare the data from the penguins


## Results

I first created a scatterplot in which I am seeing if there is a trend between bill depth and bill length within the three islands. 
```{r}
length_and_depth <- ggplot(data = penguins) +
  geom_point(mapping = aes(x = bill_length_mm, y = bill_depth_mm, color = island))
length_and_depth
```

I next added best fit lines to get a better view of what the trend actually is in each island. 
```{r}
length_and_depthline <- ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = island)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship Between Size Measurements and Island",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)")
length_and_depthline
```

For another comparison, I looked at the trend between flipper length and body mass of the penguins and what island they lived on.

```{r}
flipper_and_mass <- ggplot(data = penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = island))
flipper_and_mass
```

I again added best fit lines to this graph also. 

```{r}
flipper_and_massline <- ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = island)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship Between Size Measurements and Island",
       x = "Flipper Length (mm)",
       y = "Body Mass (g)")
flipper_and_massline
```

I also wanted to compare just one numerical variable of flipper length of the penguins to what island that they lived on, so I created a boxplot, which showed that the island of Biscoe had penguins with the longest flipper length. 

```{r}
flipper_boxplot <- ggplot(penguins, aes(x=island, y=flipper_length_mm, color = island)) +
  geom_boxplot(notch=FALSE, outlier.colour="cadetblue3", outlier.shape=8,
               outlier.size=4)
flipper_boxplot
```


## Discussion
